---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Stat545B2

<!-- badges: start -->
<!-- badges: end -->

This package is developed as an assignment B-2 for the STAT 545B course.
Give 'delta()' function to find the differences between maximum and minimum values.

## Installation

Stat545B2 is not yet on CRAN. But, you can download it from this repository using the following R command:

``` r
devtools::install_github("SereniT33/packageSereniT33")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(Stat545B2)
library(datateachr)
library(tidyverse)
pivoted_flow_sample <- flow_sample %>%
  pivot_wider("year", names_from = "extreme_type", values_from = "flow") %>%
  group_by(year) %>%
  mutate(maximum = as.numeric(maximum)) %>%
  mutate(minimum = as.numeric(minimum)) 

delta(pivoted_flow_sample, "maximum", "minimum")
```

Note that this package requires the data set that has columns for maximum and minimum values for each observation, in this case, year. 
